### 2019-01-02 writing/thesis/chapters/results.tex
Add some plans for further results.

\section{Accurate CFD}
\section{Accurate Clouds}
\section{AMR Efficiency}
To show the effectiveness of the \amr{}, we compare the time to solution of a simulation using \amr{} and another simulation with a fully refined mesh.
In detail, we compare
\begin{description}
\item[AMR] We use a coarse mesh with just $9 \times 9$ cells.
  Each cell can be refined up to three times.
  That is, the cells have sidelengths of roughly $\left( \SI{111.1}{\m}, \SI{37.04}{\m}, \SI{12.35}{\m} \right)$.
  As refinement thresholds we use $T_\text{refine} = 2.5$ and $T_\text{delete} = -0.5$ in \cref{eq:refinement-criterion}.
\item[Fine] We use a uniform grid where all cells have a sidelength corresponding to the finest mesh of the \amr{}-test case.
  In addition, we disable the reduction of global observables.
\end{description}
We use an \aderdg{}-method of order $4$ and thus have a minimal effective resolution of ca.\ $\SI{3.09}{\m}$.

@@

We use a single node of the Haswell-nodes of the Supermuc (Phase 2).
The node has two xxx \textsc{cpu}s with 28 cores each.
We use the \tbb{} parallelisation of \exahype{}.
To find a reasonable parameter for the number of background threads, we ran a grid search.
We ran three \arm{} testcases for a simulation time of $\SI{1}{\min}$.
The best median performance was achieved by only using two background threads!

\section{Reactive Euler \textit{\&} Navier Stokes}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../main"
%%% End:

>>>>

\section{Accurate CFD}
Show:
\begin{itemize}
\item Taylor-Green High Order
\item ABC Medium Order
\end{itemize}
\section{Accurate Clouds}
\begin{itemize}
\item Cosine Bubble
\item Two Bubbles
\end{itemize}
\section{Time-to-solution: AMR vs Static Mesh}
To show the effectiveness of the \amr{}, we compare the time to solution of a simulation using \amr{} and another simulation with a fully refined mesh.
In detail, we compare
\begin{description}
\item[AMR] We use a coarse mesh with just $9 \times 9$ cells.
  Each cell can be refined up to three times.
  That is, the cells have sidelengths of roughly $\left( \SI{111.1}{\m}, \SI{37.04}{\m}, \SI{12.35}{\m} \right)$.
  As refinement thresholds we use $T_\text{refine} = 2.5$ and $T_\text{delete} = -0.5$ in \cref{eq:refinement-criterion}.
\item[Fine] We use a uniform grid where all cells have a sidelength corresponding to the finest mesh of the \amr{}-test case.
  In addition, we disable the reduction of global observables.
\end{description}
We use an \aderdg{}-method of order $4$ and thus have a minimal effective resolution of ca.\ $\SI{3.09}{\m}$.

@@

We use a single node of the Haswell-nodes of the Supermuc (Phase 2).
The node has two xxx\todo{name cpus} \textsc{cpu}s with 28 cores each.
Both \textsc{cpu}s currently run on \SI{1.8}{\GHz}
We use the \tbb{} parallelisation of \exahype{}.
To find a reasonable parameter for the number of background threads, we ran a grid search.
We ran three \amr{} testcases for a simulation time of \SI{1}{\min}.
\todo{Noisy, show results}
The best median performance was achieved by using seven background threads.

\section{Reactive Euler \textit{\&} Navier Stokes}
\begin{itemize}
\item With viscous effects
\item Without viscous effects  
\end{itemize}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../main"
%%% End:
